---
title: "eda"
author: "Vinayak P Bhupal & Sanjeev VVS"
date: '2022-06-26'
output:
  pdf_document: default
  html_document:
    df_print: paged
---

**IMPORTING THE GIVEN DATASETS FROM THE EXCEL AFTER DOWNLOADING IT INTO THE LOCAL SYSTEM**

```{r}

library(readxl)
data<-read_excel("Desktop/edala1dts.xlsx")
data
```

**SUMMARY OF THE IMPORTED DATASET**

```{r}
summary(data)
```

**structure of the dataset, usually used to examine the structue of the object and also returns the number of rows and columns**

```{r}
str(data)
```

**class(data) command is used to know the type of the object**

```{r}
class(data)
```

**as.facotr/as.character converts the current object data type into respective one**

```{r}
x<-as.factor(data$Liked)
x
class(x)
y<-as.character(x)
class(y)
```

    commands for displaying the columns as per mentioned in command

**output based the column number mentioned in the command** *displaying just first column*

```{r}
data[1]
```

*displaying second columns column*

```{r}
data[2]
```

*displaying the first & second column separately with just five records*

```{r}
data[1:5,1]
data[1:5,2]
```

**Prints all columns except first column**

```{r}
   data[-1];
```

**Prints total number of columns**

```{r}
   length(data)
```

**using max function to know the max value in the particular column** *1 is the maximum value in the column*

```{r}
max(data$Liked)
```

**The seq R function generates a sequence of numeric values.**

```{r}
   data[seq(2,length(data),5)]
```

**sort function returns the results sorted in ascending order. we can use a minus sign to get results in descending order**

```{r}
sort(data$Review)
```

order function in R returns the position of each element of its input in ascending or descending order.

```{r}
  order(data$Review)
```

**rank function will return a dataframe providing the rank of each element within a dataframe**

```{r}
rank(data$Review)
```

**the head and tail function gives the first and last few rows, the number of records displyed can also be expicitly specified by the argument n which indicates the number of records that need to be submitted**

```{r}
head(data)
head(data, n=3)
tail(data)
tail(data,n=3)
```

**gives all the column names of data frame value**

```{r}
  names(data) 
```

**row names** *in this case the rows are classified by numbering which is choosen as the default row names*

```{r}
row.names(data)
```

**dimnames return both row and column names**

```{r}
dimnames(data)
```

**converting the dataframe into matrix and list using as.matrix/list functions**

```{r}
d1=as.matrix(data)
d1
d2=as.list(data)
d2
```

**the quantile() function in R can be used to calculate sample quantiles of the dataset**

```{r}
quantile(data$Liked)
```

**to calculate the five-number summary in the R programming language, we use fivenum() function**

```{r}
fivenum(data$Liked)
```

**calculating quantiles at 20%,25%,50%,75% and 80%**

```{r}
quantile(data$Liked,c(0.2,0.25,0.5,0.75,0.8))
```

**cumulative min and max functions will have the following output**

```{r}
cummax(data$Liked)
cummin(data$Liked)
```

**ggplot of the given column in datasets for visual representation** *geom function is used to visualize the distribution of a single continuous variable*

```{r}
library(ggplot2)
ggplot(data,aes(x=Liked))+geom_histogram(fill="red",colour="black")
  
```

**facet function is used to divide the entire dataset according to categorical variables**

```{r}
library(ggplot2)
ggplot(data,aes(x=Liked))+geom_histogram(fill="red",colour="black")+facet_grid(Liked~.)
  
```

**Loading library dplyr. and adding new column to the value data frame. we use mutate function to add new column**

**new column is created using if else function where if liked is 1 then "good" is updated or its "bad"**

```{r}
  library(dplyr);
temp=data %>% mutate(overall=if_else(Liked==1,"good","bad"))
```

**selecting a record based on the column values**

```{r}
data %>% filter(Review=="The fries were great too." & Liked==1)
```

**renaming the existing column name. for that we use rename function.**

```{r}
data %>% rename(Rating=Liked)
```

**visualization of points on line graph**

```{r}
ggplot(data,aes(x=Review,y=Liked))+geom_line()+geom_point()
```

```{r}
ggplot(data,aes(x=Review, y=Liked))+geom_line()+geom_point()
```

**visualization of bar graph of values.**

```{r}
ggplot(data,aes(x=Review, y=Liked))+geom_col()
```

**visualization of bar graph of counts.**

```{r echo=TRUE, warning=FALSE}
ggplot(data,aes(x=Review))+geom_bar()

```


