---
title: "EDA la2"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
date: '2022-07-03'
---





```{r}


library(readxl)
Restaurant_la <- read_excel("C:/Users/Admin/Desktop/Restaurant_la.xlsx")
View(Restaurant_la)
```



**Visualizations of dataset in BAR Graph**
```{r}
library(ggplot2)
ggplot(Restaurant_la,aes(x=Review))+geom_bar()
```
**Visualizations of dataset in BAR Graph**
```{r}
ggplot(Restaurant_la,aes(x=Liked))+geom_bar()
```

**Visualizations of dataset in histogram Graph**
```{r}
ggplot(Restaurant_la,aes(x=Liked))+geom_histogram()
```
**Visualizations of dataset in ScatterPlot**
```{r}
ggplot(Restaurant_la,aes(x=Review,y=Liked))+geom_point()
```

**Visualizations of dataset in Vilion Graph**
```{r}
ggplot(Restaurant_la,aes(x=Review,y=Liked))+geom_violin()
```

**Visualizations of dataset in Line Graph**
```{r}
ggplot(Restaurant_la,aes(x=Review,y=Liked))+geom_line()
```
**Visualizations of dataset in Poly_Freq Graph**
```{r}
ggplot(Restaurant_la,aes(x=Liked))+geom_freqpoly()
```

**Visualizations of dataset in Density Graph**
```{r}
ggplot(Restaurant_la,aes(x=Review,y=Liked))+geom_density()
```
**Density curves with facets**
```{r}
ggplot(Restaurant_la, aes(x = Liked)) +
  geom_density() +
  facet_grid(Liked ~ .)
```
**Density curves overlaid on histograms**
```{r}
ggplot(Restaurant_la, aes(x = Liked)) +
  geom_histogram(binwidth = 200, fill = "cornsilk", colour = "grey60",
                 size = .2) +
  geom_density() +
  facet_grid(Liked ~ .)
```

**#Making a Basic Box Plot**
```{r}
ggplot(Restaurant_la, aes(x = Review,y=Liked)) +  geom_boxplot()
```
**#Box plot with narrower boxes**
```{r}
ggplot(Restaurant_la, aes(x = Review, y = Liked)) +  geom_boxplot(width = .5)
```

**#Making Multiple Dot Plots **
```{r}
ggplot(Restaurant_la, aes(x = Review, y = Liked)) +
  geom_dotplot(binaxis = "y", binwidth = .5, stackdir = "center")
```



